# Scrape using the NET/RPI ratings

This method uses a directly addressable link to the national NET/RPI rankings for every Division I program. The table contatins the link to each team's season page which is identital to the one in the CSV in the other method. The upside of this method is that there is no manual process so it's more automated. The downside is that NET ratings don't start until mid-season. 

This file exists to be able to debug scrapers incrementally using the notebook's block formatting. Steps can be cut out, tested and improved then cycled back into the scripts. The scripts are doing the scraping -- I use R Studio jobs to run them in the background. 

```{r}
library(tidyverse)
library(lubridate)
library(rvest)
library(janitor)
```
Here are the addressable urls to NET/RPI rankings for the three years available:

2019: http://stats.ncaa.org/selection_rankings/nitty_gritties/13983
2020: http://stats.ncaa.org/selection_rankings/nitty_gritties/21145
2021: http://stats.ncaa.org/selection_rankings/nitty_gritties/23024



```{r}
url <- "http://stats.ncaa.org/selection_rankings/nitty_gritties/21145"

urllist <- url %>% 
  read_html() %>%
  html_nodes(xpath = '//*[@id="selection_rankings_nitty_gritty_data_table"]') %>% 
  html_elements("a") %>%
  html_elements(xpath = '//*[@target="TEAM_PAGE"]') %>%
  html_attr('href') %>%
  as_tibble() %>%
  mutate(value = paste0("https://stats.ncaa.org", value))

urls <- pull(urllist, 1)
```

```{r}
root_url <- "https://stats.ncaa.org"
season = "2020"
playerstatstibble = tibble()
gamestatstibble = tibble()

playerstatsfilename <- paste0("ncaa_volleyball_playerstats_", season, ".csv")
gamestatsfilename <- paste0("ncaa_volleyball_gamestats_", season, ".csv")
```

```{r}
for (i in urls){

schoolpage <- i %>% read_html()

schoolfull <- schoolpage %>% html_nodes(xpath = '//*[@id="contentarea"]/fieldset[1]/legend/a[1]') %>% html_text()

roster_url <- schoolpage %>% html_nodes(xpath = '//*[@id="contentarea"]/a[1]') %>% html_attr('href')

playerstats_url <- schoolpage %>% html_nodes(xpath = '//*[@id="contentarea"]/a[2]') %>% html_attr('href')

gamestats_url <- schoolpage %>% html_nodes(xpath = '//*[@id="contentarea"]/a[3]') %>% html_attr('href')

playerstats <- paste(root_url, playerstats_url, sep="") %>% read_html() %>% html_nodes(xpath = '//*[@id="stat_grid"]') %>% html_table()

tryCatch(playerstats <- playerstats[[1]] %>% filter(Player != "TEAM" & Player != "Totals" & Player != "Opponent Totals") %>% mutate(RosterName = Player) %>% separate(Player, into=c("LastName", "FirstName"), sep=",") %>% mutate(FullName = paste(FirstName, LastName, sep=" ")) %>% separate(Ht, into=c("Feet", "Inches"), sep="-") %>% mutate(Team = schoolfull, Season=season) %>% clean_names() %>% select(team, season, jersey, full_name, roster_name, everything()) %>% mutate_at(10:31, ~str_replace(., ",", "")) %>%  mutate_at(10:31, as.numeric),
    error = function(e){NA})

tryCatch(playerstatstibble <- bind_rows(playerstatstibble, playerstats),
    error = function(e){NA})

gamepage <- paste(root_url, gamestats_url, sep="") %>% read_html() 

games <- gamepage %>% html_nodes(xpath = '//*[@id="game_breakdown_div"]/table') %>% html_table(fill=TRUE)

tryCatch(games <- games[[1]] %>% slice(3:n()) %>% filter(X2 != "Defensive Totals") %>% row_to_names(row_number = 1) %>% remove_empty(which="cols") %>% mutate(Date = mdy(Date), HomeAway = case_when(grepl("@",Opponent) ~ "Away", TRUE ~ "Home"), Opponent = gsub("@ ","",Opponent), WinLoss = case_when(grepl("L", Result) ~ "Loss", grepl("W", Result) ~ "Win"), Result = gsub("L ", "", Result), Result = gsub("W ", "", Result)) %>% separate(Result, into=c("VisitorScore", "HomeScore")) %>% rename(Result = WinLoss) %>% mutate(Team = schoolfull) %>% select(Date, Team, Opponent, HomeAway, Result, everything()) %>% clean_names() %>% mutate_at(vars(-date, -opponent, -home_away, -result, -team), ~str_replace(., "/", "")) %>% mutate_at(vars(-date, -opponent, -home_away, -result, -team), as.numeric),
    error = function(e){NA})

tryCatch(gamestatstibble <- bind_rows(gamestatstibble, games),
    error = function(e){NA})

Sys.sleep(2)
}

playerstatstibble <- playerstatstibble %>% remove_empty(which="rows")
gamestatstibble <- gamestatstibble %>% remove_empty(which="rows")

write_csv(playerstatstibble, playerstatsfilename)
write_csv(gamestatstibble, gamestatsfilename)
```